A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2021-02-10 05_severity_metaAnalysis.Rmd
Update object names and input MA estimates table

if (!require("theme.usq"))
   devtools::install_github("adamhsparks/theme.usq")
library(theme.usq)
theme_set(theme_usq())
#source(here("R/reportP.R"))

@@

>>>>

if (!require("theme.usq"))
   devtools::install_github("adamhsparks/theme.usq")
library(theme.usq)
theme_set(theme_usq())
source(here("R/reportP.R"))

@@

```{r metafor_results}
# obtain number of treatments included in each moderator variable
k5 <-
   as.data.frame(table(PM_dat_D$trial, PM_dat_D$spray_management)) %>%
   filter(Freq != 0) %>%
   group_by(Var2) %>%
   summarise(n()) %>%
   pull()

# create data.frame
results_mv <- data.frame(
   N = PMsev_mv$g.levels.k,
   k = k5,
   Effect = round(PMsev_mv$b, 4),
   se = round(PMsev_mv$se, 4),
   CI_lower = round(PMsev_mv$ci.lb, 4),
   CI_upper = round(PMsev_mv$ci.ub, 4),
   z_val = round(PMsev_mv$zval, 4),
   p_val = reportP(PMsev_mv$pval, AsNumeric = TRUE)
)

# rename colnames to give table headings
colnames(results_mv)[c(1:4, 6:9)] <-
   c("Treatment",
     "$N$",
     "$k$",
     "$\\mu$",
     "$CI_{L}$",
     "$CI_{U}$",
     "$Z$",
     "$P$")

# provide rownames for each moderator variable
row.names(results_mv) <- c(
   "Intercept / No Spray control",
   "$Early_{single}$",
   "$Recommended_{single}$",
   "$Recommended_{plus}$",
   "$Late_{single}$",
   "$Late_{plus}$"
)

kable(results_mv[2:6, 2:9],
      align = "lcccccccc",
      booktabs = TRUE,
      caption = "Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment. Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of field trials undertaken in Eastern Australia. Z and P values indicate statistical significance in comparison to the intercept.")
```
